---
title: "Limiting, Proportion of Unmet Need"
output: github_document
author: Leontine Alkema and Greg Guranich 
---

## Project Background
We are estimating the proportion of limiting within unmet need for contraceptives (country level proportions). Limiting is when a women wishes not to have children anymore. Spacing is when a women wishes not to have children for a specified term

## SETUP
- clone the repository to your local machine
- create R project from existing directory (chose this folder "~/limiting_advr")
- Open README.rmd this is the master script!
- run the code block labeled 'REQUIRED SETUP'
- do not run any more of master script, briefly look at the master script if you like
- open whichever subscript to get started!
- subscripts (that may be turned into R functions) begin with "sub_"

## Directories
- /R ~ functions
- /data ~ data
- /output_sample ~ sample model files for you to work with

## .gitignore Directories
The following full directories are not shared on git due to size contraints

- /output ~ model files (by runname), 
- /formal ~ Latex scripts, associated image files, documentation of math
- /fig ~ image files


# REQUIRED SETUP
```{r, eval = FALSE}
demandestimates.dir <- "data/demandnew.csv" #data produced by a model
cprestimates.dir <- "data/cpr.csv"
countryinfo.dir <- "data/Country-and-area-classification.csv"
rawdata_dhs.dir <- "data/dhs_2018_edit.csv"
rawdata_mics.dir <- "data/mics_2018_edit.csv"
fp20.dir<- "data/fp2020.csv" #list countries in fp2020 if we wish to subset

Rfiles <- list.files(file.path(paste0(getwd(),"/R/")), ".R") 
sapply(paste0(paste0(getwd(),"/R/"), Rfiles), source) 
source("sub_loadpackages.R")

SSA <- FALSE
NOTSSA <- FALSE
startyear <- 1985
#startyear <- 2007
endyear <- 2020 #2020 #2030 # earlier end year for testing (less time to run jags)
nyears <- endyear - startyear + 1
do.validation <- FALSE
addarma <- FALSE
```

# testing pull request again 4
```{r, eval = FALSE, include = FALSE}
runname <- "model2_spline00"
MakeDirs(runname)
output.dir <- MakeDirs(runname)

source("sub_readandprocessdata.R")
parnames <- c("yrepluup.i","a.c","beta.c", "eta.j")

# if (SSA == TRUE) {
#   model.file <- WriteModel2SSA(output.dir, modelname = "model", addarma  = addarma)
# } else {
#   model.file <- WriteModel2(output.dir, modelname = "model", addarma  = addarma)
# }
model.file <- WriteModel2_splines02(output.dir, modelname = "model", addarma  = addarma)

file.show(model.file)
mod <-jags.parallel(data = jagsdata, inits = inits(), #NULL,
                    parameters.to.save=parnames,
                    model.file = model.file,
                    n.chains=4, n.burnin = 2000, n.iter = 10000, n.thin = 8)
#                   n.chains=4, n.burnin = 1000, n.iter = 3000, n.thin = 2) # 
#     n.chains=3, n.burnin = 500, n.iter = 1000, n.thin = 2) # test
#     n.chains=2, n.burnin = 5, n.iter = 10, n.thin = 1) # test

saveRDS(mod, file = paste0(output.dir, "mod.rds"))
# if you need to reload it:
#mod <- readRDS(file = paste0(output.dir, "mod.rds"))
mcmc.array <- mod$BUGSoutput$sims.array

#source("sub_convergence.R")
#source("sub_residuals.R")
#source("sub_timeplot.R")
#source("sub_validationoutput.R")
source("sub_postproc_forEDA.R")
```


## To do list ...
### DATA PREP FOR MODEL
Nutcha

Feature engineering/cleaning

<!-- -make data frames that break down data by group ~ hold off on this -->
<!-- 	-unit level data (country) -->
<!-- 	-link from unit to next level (subregion) -->
<!-- 	-link to next parent (region) -->

-dynamic code to choose subsets of data, interacts with main script
	-subsets for area
	-SSA (sub saharan africa)
	-Non SSA
	-All
	-subsets of time

Greg

-making index for jags
	-ie. Getc.i, gett.i, getr.c, ...
-most important for checks (function testing)

Making the jags object
-to dp…

...Run model


Yash

-residual plot ....
-country fits plots
-make code into function that allows user to specify parameter of interest
-function to get point estimates from jags output (median, and CI)
-function to merge output of the above function with data
	-data can be found in jags object

Streamline other model validation

-LOO
-rhat

Plotting code that use non standard evaluation (NSE)
-send document to yash and nutcha
https://dplyr.tidyverse.org/articles/programming.html

